Future Evolution of CSMA Protocols for the IEEE 802.11 Standard

### 2013-03-01 paper.tex
finished figure

An example of the operation of CSMA/ECA with hysteresis is presented in Fig. \ref{fig:csma_eca_different_backoff}.

>>>>

An example of the operation of CSMA/ECA with hysteresis is presented in Fig. \ref{fig:csma_eca_different_backoff}.
There are four stations in the example and the transmissions of those stations are represented as rounded boxes.
The small numbers are the value of the backoff counter of the stations, that decrement in every slot boundary.

The stations initially pick a random backoff. 
Those stations with the same backoff value collide and choose a new backoff value.
When all the stations have a different backoff value, no more collisions will occur.
At this point the behaviour of the system is cyclic and deterministic.
Note that the state of the system at the beginning of the cycle is the backoff counter of the four stations: 4, 9, 14 and 2.
It is exactly the same state that the first slot of the next cycle.

The length of the cycle (32 slots) is indicated by the arrows at the bottom of the figure.
The stations that collide double their contention window, the deterministic backoff after successes and the number of transmitted packet in each transmission attempt.
